%=========================================================
\chapter{Bibliografía}

\begin{description}
	
		\item[\hypertarget{b01}{[1]}] Rui, K. Butler, G. (2003, April 21). Refactoring use case models: the metamodel [Online]. Available: https://dl.acm.org/citation.cfm?id=783140
		
		\item[\hypertarget{b02}{[2]}] Shuang, L. Sun, L. (2014, September 19). Automatic early defects detection in use case documents [Online]. Available: https://dl.acm.org/citation.cfm?id=2642969
		
		\item[\hypertarget{b03}{[3]}] 
		J. Lee. (1999, August). Analyzing user requirements use cases a goal driven approach. [Online]. Avaible: https://ieeexplore.ieee.org/document/776956
		
		\item[\hypertarget{b04}{[4]}]  L. Julijana. (2007, August). “Information Systems Modeling with Use Cases” IEEE Computer [Online]. Available:
		https://ieeexplore.ieee.org/document/4283759
		
		\item[\hypertarget{b05}{[5]}] Jason Gorman, J. G. (2007, 9 marzo). 10 Common Use Case Pitfalls. Recuperado 23 abril, 2018,  [Online]. Available: http://codemanship.co.uk/parlezuml/blog/?postid=364
		
		\item[\hypertarget{b06}{[6]}] Susan Lilly [2002, August]. “Use Case Pitfalls: Top 10 Problems from Real Projects Using Use Cases” [Online]. Avaible: https://ieeexplore.ieee.org/document/787547
		
		\item[\hypertarget{b07}{[7]}] Universidad Michoacana de San Nicolás de Hidalgo. (2014): “Competitividad y factores de éxito en empresas desarrolladoras de software” [Online]. Avaible: https://dialnet.unirioja.es/servlet/articulo?codigo=5101928
		
		\item[\hypertarget{b08}{[8]}] Mr. Vikas S. Chomal, Dr. Jatinderkumar R. Saini, (2014). “Significance of Software Documentation in Software
		Development Process“
 / (7 páginas). International Journal of Engineering Innovation and Research. 
		
		\item[\hypertarget{b09}{[9]}] Pressman, Roger. (2010). Ingenieria de Software. Un enfoque práctico / 7 ED.(777 páginas). USA: Mcgraw-Hill Interamericana.
		
		\item[\hypertarget{b10}{[10]}] B. Imran S. and H. Irfan, "UCD-generator - a LESSA application for use case design - IEEE Conference Publication", Ieeexplore.ieee.org, 2007. [Online]. \\Available: https://ieeexplore.ieee.org/document/4381333.
		
		\item[\hypertarget{b11}{[11]}] G. Booch, J. Rumbaugh, I. Jacobson, J. García Molina and J. Saez Martínez, El lenguaje unificado de modelado, 2nd ed. Madrid: Pearson Educación, 2010.
		
		\item[\hypertarget{b12}{[12]}] D. West, "Use Cases Considered Valuable (but Optional) For Lean/Agile Requirements Capture", InfoQ, 2010. [Online]. Available: https://www.infoq.com/news/2009/02/Use-Cases-Valuable-But-Optional. 
		
		\item[\hypertarget{b13}{[13]}] D. González, "Industria Mexicana del Software. Un estudio en cifras.", SG Buzz, 2005. [Online]. Available: https://sg.com.mx/revista/9/industria-mexicana-cifras. [Accessed: 20- Apr- 2019].
		
		\item[\hypertarget{b14}{[14]}] J. Gómez, "Métodos de Medición en Puntos Función (I): IFPUG FPA", El Laboratorio de las TI, 2014. [Online]. Available: https://www.laboratorioti.com/2013/01/16/metodos-de-medicion-en-puntos-funcion-i/. 
		
		\item[\hypertarget{b15}{[15]}] Ganesh Krishnamurthy, "CASE Tools 
		Adoption and Relevance" University of Missouri–St. Louis [Online]. Available: http://www.umsl.edu/~sauterv/analysis/F08papers/View.html
		
		\item[\hypertarget{b16}{[16]}] Annette L. du Plessis, A method for CASE tool evaluation, Information and Management, Volume 25, Issue 2, August 1993, Pages 93-102
		
		\item[\hypertarget{b17}{[17]}]	Erich Gamma, "Patrones de diseño: elementos de software orientado a objetos reutilizable", Pearson Educación, 2002. Addison-Wesley professional computing series.
		
		\item[\hypertarget{b18}{[18]}] IBM Knowledge Center, "Patrón de diseño de modelo-vista-controlador" [Online].\\ Available: https://www.ibm.com/support/knowledgecenter/es
		
		\item[\hypertarget{b19}{[19]}] Christopher Alexander, Sara Ishikawa, MurraySilverstein, Max Jacobson,
		Ingrid Fiksdahl-King, and Shlomo Angel.A Pattern Language. Oxford University
		Press, NewYork, 1977.
		
		\item[\hypertarget{b20}{[20]}] Glenn E. Krasner and Stephen T. Pope. A cookbook for using the model-view
		controller user interface paradigm in Smalltalk-80. Journal of Object-Oriented Programming, 1(3):26–49, August/September 1988.
		
		\item[\hypertarget{b21}{[21]}] BBVA-TRANSFORMACIÓN DIGITAL, "Metodología 'scrum': ¿Qué es un 'sprint'?", [Online].\\ Available: https://www.bbva.com/es/metodologia-scrum-que-es-un-sprint/
		
		\item[\hypertarget{b22}{[22]}] Proyectos Agiles, "Lista de tareas de la iteración (Sprint Backlog)", [Online].\\ Available: https://proyectosagiles.org/lista-tareas-iteracion-sprint-backlog/
		
		\item[\hypertarget{b23}{[23]}] Clemente Ruiz Durán, Michael Piore
		Andrew Schrkarn, "Los retos para el desarrollo
		de la industria del software", [Online].\\ Available: http://revistas.bancomext.gob.mx/rce/magazines/87/1/Ruiz-Schrank.pdf

		\item[\hypertarget{b24}{[24]}] Universidad Católica de los Angeles Chimbote-PERÚ, "Metodología de Desarrollo de Software"  [Online].\\ Available: https://www.uladech.edu.pe/images/stories/universidad/documentos/2018/metodologia-desarrollo-software-v001.pdf
		
		\item[\hypertarget{b34}{[34]}] ISTQB (International Software Testing Qualifications Board), "Foundations of Software Testing" [Online].\\ Available: 
		https://www.istqb.org/downloads/send/51-ctfl2018/208-ctfl-2018-syllabus.html
		
		\item[\hypertarget{b35}{[35]}] ISTQB (International Software Testing Qualifications Board), "Certified Tester
		Foundation Level Syllabus", 2018 Version 
		
		\item[\hypertarget{b36}{[36]}] Campell / Papapetrou, Ann / Patroklos (2013). Sonar (SonarQube) en acción . Greenwich, Connecticut, EE. UU .: Manning Publications. pags. 350. ISBN 978-1617290954.
		
		\item[\hypertarget{b37}{[37]}] Buijze, Allard (26 de febrero de 2010). "Medición de la calidad del código con sonda" . Consultado el 29/08/2017 .
				
		\item[\hypertarget{b25}{[25]}] (https://docs.spring.io/spring-framework/docs/current/spring-framework-reference/data-access.html\#transaction)
		
		\item[\hypertarget{b26}{[26]}] (https://docs.spring.io/spring-framework/docs/current/spring-framework-reference/data-access.htmlt\#ransaction-declarative)
		
		\item[\hypertarget{b27}{[27]}] https://struts.apache.org/birdseye.html 
		
		\item[\hypertarget{b28}{[28]}] https://struts.apache.org/primer.html\#mvc
		
		\item[\hypertarget{b29}{[29]}]
		https://struts.apache.org/core-developers/interceptors.html\#order-of-interceptor-execution
		
		\item[\hypertarget{b30}{[30]}] 	https://www.researchgate.net/profile/Praveen\_Gupta25/publication/49619227\_MVC\_Design\_Pattern\_for\_the\_multi\_framework\_distributed\_applications\_using\_XML\_spring\_and\_struts\_framework/links/5672564e08ae54b5e462aac5.pdf
		
		\item[\hypertarget{b31}{[31]}] (https://link.springer.com/chapter/10.1007/978-1-4302-2370-2\_20)
		\item[\hypertarget{b32}{[32]}] (https://docs.microsoft.com/es-es/azure/architecture/guide/architecture-styles/n-tier)
		\item[\hypertarget{b33}{[33]}](https://docs.spring.io/spring/docs/3.0.0.M3/reference/html/ch04s04.html\#beans-factory-scopes-singleton)

\end{description}